### 2014-02-14 brains-protocol.tex
Add a todo for classical psycholinguistic features
Some additional answers for fact-checks

@@

While the original WN network is a weighted, undirected network, the FA network is a directed network where weights have a different meaning.
Both semantic networks describe synonymy relationships corresponding to qualitatively distinct forms of association: either from a linguistic viewpoint (WN) or from the perspective of actual information retrieval by humans (FA).
In  order to work in a unified framework, we shall consider links as an information on the existence of some sort of association between two words and transform both networks into undirected, unweighed networks.
\rk{Check that's the case in the analysis}

@@

Additionally, number of phonemes and number of syllables exhibit a strong linear correlation ($0.85$).
The analysis showed a better prediction effect of number of phonemes over number of syllables, which is consistent with~\citet{nick-diss}, and we therefore chose to focus the presented results on the former only.
\rk{Check that!}

>>>>

\rk{Add some bibliography about those features' known effects}

@@

While the original WN network is a weighted, undirected network, the FA network is a directed network where weights have a different meaning.
Both semantic networks describe synonymy relationships corresponding to qualitatively distinct forms of association: either from a linguistic viewpoint (WN) or from the perspective of actual information retrieval by humans (FA).
In  order to work in a unified framework, we shall consider links as an information on the existence of some sort of association between two words and transform both networks into undirected, unweighed networks.
\rk{Check that's the case in the analysis}
\rk{In fact, the graphs are much less interesting for undirected unweighed FA.}

@@

Additionally, number of phonemes and number of syllables exhibit a strong linear correlation ($0.85$).
The analysis showed a better prediction effect of number of phonemes over number of syllables, which is consistent with~\citet{nick-diss}, and we therefore chose to focus the presented results on the former only.
\rk{Rather, graphs are much nicer with number of phonemes than number of syllables: clearer tendencies, more data (there's holes with number of syllables). But not a prediction (prediction of what?)}
